\section{About Project}
\subsection{Title}
\noindent The title of the project is \textbf{AI Resume Builder}.

\subsection{Domain}
\noindent The project belongs to the domains of artificial intelligence, full-stack web application development, and career support systems.

\subsection{Aim}
\begin{itemize}
\item To provide a single platform for generating structured resumes from unstructured user input.
\item To help users tailor resumes against job descriptions and identify missing keywords.
\item To support professional job preparation with interview questions, email drafting, and profile-based resume history.
\item To reduce manual effort in formatting, exporting, and maintaining multiple resume versions.
\item To combine AI-assisted writing with practical recruiter-facing workflows in one application.
\end{itemize}

\subsection{Objectives}
\begin{itemize}
\item Build a responsive frontend using React and Vite for resume creation, editing, and preview \cite{react_docs,vite_docs}.
\item Develop a Spring Boot backend that exposes secure endpoints for generation, upload analysis, profile access, and job search \cite{spring_boot_docs,spring_security_docs}.
\item Integrate Ollama through Spring AI to generate resumes, tailoring insights, and interview support \cite{spring_ai_docs,ollama_docs}.
\item Support upload-based ATS-style analysis for TXT, PDF, and DOCX resumes by using PDFBox, pdf.js, and Apache POI \cite{pdfbox_docs,pdfjs_docs,poi_docs}.
\item Enable template selection, PDF export, and saved resume history for authenticated users.
\end{itemize}

\subsection{Problem Statement}
\noindent Candidates often maintain resumes in static documents that are difficult to update, customize, or compare against job descriptions. Existing lightweight resume tools usually stop at formatting, while AI writing tools rarely provide structured templates, score-based review, saved history, and interview preparation in one consistent workflow. The problem addressed by this project is the lack of an integrated system that can generate a well-structured resume, adapt it for a target role, evaluate uploaded resumes, and preserve multiple recruiter-ready versions for future use.
