\section*{Plagiarism Report}
\noindent This project report titled \textbf{AI Resume Builder} has been checked using a plagiarism-detection tool before final submission. The purpose of this verification is to ensure that the report content is original, properly paraphrased where required, and supported by appropriate citations for referenced technical material, frameworks, and documentation.

\subsection*{Plagiarism Check Summary}
\begin{table}[H]
\centering
\caption{Plagiarism report summary}
\begin{tabular}{|p{4.5cm}|p{7.0cm}|}
\hline
\textbf{Parameter} & \textbf{Details} \\
\hline
Project Title & AI Resume Builder \\
\hline
Student Name & [Student Name] \\
\hline
Exam Seat Number & [Seat Number] \\
\hline
Department & Master of Computer Applications \\
\hline
Plagiarism Checking Tool & [Tool Name] \\
\hline
Date of Check & [DD / MM / YYYY] \\
\hline
Overall Similarity Index & [\% Similarity] \\
\hline
Permissible Limit & [College / University Limit] \\
\hline
Final Status & [Acceptable / Needs Revision] \\
\hline
\end{tabular}
\end{table}

\subsection*{Interpretation}
\noindent The similarity result should be interpreted together with citation quality and the nature of matched text. Technical documents often contain unavoidable similarity in framework names, API terminology, standard definitions, and bibliography entries. Such matches do not necessarily indicate plagiarism when they are properly referenced and used in context. The final report should therefore be reviewed not only for numerical similarity percentage, but also for originality of explanation, project-specific analysis, and correct attribution.

\subsection*{Declaration on Originality}
\noindent The developed system, analysis, design descriptions, implementation details, diagrams, and testing discussion in this report are prepared specifically for the \textbf{AI Resume Builder} project. Wherever external ideas, tools, or documentation have been referred to, those sources are acknowledged in the references section of the report. Any final plagiarism certificate or generated similarity screenshot may be attached below or inserted on the next page at the time of official submission.

\subsection*{Attachment Placeholder}
\noindent Attach the official plagiarism report issued by the checking tool or institution here. If available, insert:
\begin{itemize}
\item similarity percentage screenshot,
\item report ID or scan reference number,
\item date and time of report generation,
\item approval or signature block if required by the department.
\end{itemize}
